|

### 2022-06-14 draft-1.Rmd
Draft formatting

output:
  officedown::rdocx_document:
    number_sections: false
    reference_docx: template.docx
    tables:
      style: stat_table
    plots:
      align: center
    page_size:
      width: 8.5
      heigh: 11
    page_margins:
      bottom: 1
      top: 1
      right: 1
      left: 1

lot: true
lof: true
toc: false

>>>>

output:
  officedown::rdocx_document:
    # number_sections: false
    # reference_docx: template.docx
    tables:
      # style: stat_table
      caption:
        # style: TableCaption
        pre: "Table "
        sep: ": "
    plots:
      align: center
    page_size:
      width: 8.5
      heigh: 11
    page_margins:
      bottom: 1
      top: 1
      right: 1
      left: 1

# lot: true
# lof: true
# toc: false
